### 2012-12-07 doc/description.tex
updated description addTable

>>>>

\subsection{Database Schema Evolution}
\subsubsection{AddTable}

$
\inference[AddTable(T, D)=]{\forall t \in tables(D) : t.name != T.name\\
	\forall f \in T.foreignKeys, \exists t in T.tables : f.reference == t.name
}{database(T \cup tables(D), data(D))}
$

\begin{verbatim}
op addTable : Table Database -> Database .
ceq addTable(T, D) = errDatabase("inconsistent", D) 
   if containsName(tables(D), name(T)) 
   or (foreignKeys(T) =/= [] 
   and not referencesExist(foreignKeys(T), tables(D))) .
eq addTable(T, D) = database(tables(D) T, data(D)) .
\end{verbatim}
